---
title: "Quanmod III"
author: "NTS"
date: "7/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(quantmod)
# library(tidyverse)
```

# Get Stock Price
```{r}
tsla <- getSymbols("TSLA", auto.assign = FALSE)
head(tsla)
```
### Store Closing Price (adjusted for stock splits)
```{r}
tsla_cl <- tsla$TSLA.Close
head(tsla_cl)
tsla_cl2 <- Ad(tsla)
head(tsla_cl2)
```
### What is Lag
```{r}
?lag
head(lag(tsla_cl,2))
```

### Remove Scientific Notation

```{r}
options(scipen = 9999)
```

### Create Daily % change vector
```{r}
daily_change <- tsla_cl/lag(tsla_cl,1) - 1
head(daily_change)
```

### Look at Histrogram of Percentage Change
```{r}
hist(daily_change, 40, col = 'green')
```

### Assign Buy Signal Parameter
```{r}
buy_signal <- .04
```

### Loop over all trading days (except the first)
buy_signal == parameter
tsla_cl == data
daily_change == %change
signal == 1 or 0 buy/sell

```{r}
signal <- c(NULL)
```

```{r}
for (i in 2:length(tsla_cl)){
  if (daily_change[i] > buy_signal){
    signal[i] <- 1
  } else
    signal[i] <- 0
}
head(signal, 40)
```

### Reclassify signal to an xts object (trying it to a date)

```{r}
signal <- reclass(signal, tsla_cl)
head(signal, 20)
```

### Plot Graph
```{r}
chartSeries(tsla_cl,
            type = "l",
            subset = "2011-01::2012-01",
            theme = chartTheme("white"))addCCI() #add Commodity Channel Index

addTA(signal, type = "S", col = "red")
```
